### 2015-01-16 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
Delco_2014: Added content to the hose test report

\chapter{Introduction}
\label{chap:Introduction}

@@

\subsection{Hose Stream Pattern Experiments}
\label{sec:Hose_Stream_Pattern_Experiments}

\subsection{Application Pattern Experiments}
\label{Application_Pattern_Experiments}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. Straight stream pattern is being applied, and flow path is fully established with the stairway door and the north side, west double door opened.}
\label{fig:test_19_pic}
\end{figure}

@@

\section{Hose Flow Tests}

\subsection{Tests 18 and 19}

>>>>

\chapter{Introduction}
\label{chap:Introduction}
NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire. The studies have resulted in guidance to the fire service regarding ventilation tactics. However ventilation tactics alone will not result in the complete extinguishment of the fire, fire suppression with hose streams are needed.

Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the line or if ventilation inducing hand line tactics are in practice. This research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.

This report is concerned with examining the impact of hose stream selection and the pattern in which the stream is applied on the ventilation inside a structure with various flow path configurations. Two types of experiments were conducted in order to examine the impact. First, cold flow tests were performed. These tests involved using a 0.46 m (18 in) diameter positive pressure ventilation (PPV) fan to move air through a structure with various flow path configurations. The second type of experiment involved flowing water using various stream and application patterns into a structure with flow path configurations similar to the cold flow test configurations. Air velocities measured during the hose flow experiments were compared to the velocities measured during the cold flow tests to determine the impact of hose stream and application pattern combinations on ventilation throughout the structure relative to the impact of using a 0.46 m (18 in) diameter PPV fan to move air throughout the structure.

Three types of hose streams were each applied in four different fashions during each set of hose flow experiments. The three types of hose stream patterns studied were straight stream, narrow fog stream, and wide fog stream. Water was flowed into the structure by having the hose in a static, fixed position, moving the hose line left-to-right across the room in a sweeping motion, and rotating the hose line in both the clockwise and counterclockwise directions.

@@

\subsection{Cold Flow Experimental Procedure}
\label{sec:Cold_Flow_Procedure}

\subsection{Water Flow Experimental Procedure}
\label{sec:Water_Flow_Procedure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}

@@

\section{Cold Flow Test Results}
\label{sec:Cold_Flow_Test_Results}

\section{Water Flow Test Results}
\label{sec:Water_Flow_Test_Results}
